Results

### 2019-03-01 02_analysis.Rmd
Wider session info
Add causal pathway diagram

```{r load-libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(rstan)
library(tidybayes)
library(broom)
library(ggstance)
library(patchwork)
library(pander)
library(scales)
library(janitor)
library(huxtable)
library(here)

@@

@@

```{r show-session-info, echo=TRUE}
writeLines(readLines(file.path(Sys.getenv("HOME"), ".R/Makevars")))

>>>>

```{r load-libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(rstan)
library(tidybayes)
library(broom)
library(ggstance)
library(ggdag)
library(patchwork)
library(pander)
library(scales)
library(janitor)
library(huxtable)
library(here)

@@

# Causal pathway

Our theory and hypotheses are laid out in the causal pathway below. Our outcomes (Y: % likely to donate and amount donated) "listen to" or respond to C (crackdown), which is our main treatment or exposure. Funding (F) and issue (I) serve as heuristics for donation and influence a government's decision to crack down on NGOs, hence the dual arrows to C and Y.

```{r causal-dag, fig.width=4.5, fig.height=2.5}
theory_dag <- dagify(Y ~ I + C + F,
                     C ~ I + F,
                     outcome = "F",
                     exposure = "C") %>% 
  tidy_dagitty(layout = "sugiyama")

plot_dag <- ggplot(theory_dag, aes(x = x, y = y, xend = xend, yend = yend)) +
  geom_dag_node(size = 12) +
  geom_dag_edges() +
  geom_dag_text(size = pts(9), family = "Encode Sans Condensed SemiBold") +
  scale_dag() +
  theme_ngos() +
  theme(panel.grid = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank())

plot_dag %T>% 
  print() %T>%
  ggsave(., filename = here("output", "figures", "causal-path.pdf"),
         width = 4.5, height = 2.5, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = here("output", "figures", "causal-path.png"),
         width = 4.5, height = 2.5, units = "in", type = "cairo", dpi = 300)
```

@@

```{r show-session-info, echo=TRUE, width=100}
writeLines(readLines(file.path(Sys.getenv("HOME"), ".R/Makevars")))
